---
output: github_document
---
[![Build Status](https://travis-ci.org/reconhub/recontools.svg?branch=master)](https://travis-ci.org/reconhub/recontools)
[![Build status](https://ci.appveyor.com/api/projects/status/wn4un3v2e3owts4l/branch/master?svg=true)](https://ci.appveyor.com/project/dirkschumacher/recontools/branch/master)
[![Coverage Status](https://img.shields.io/codecov/c/github/reconhub/recontools/master.svg)](https://codecov.io/github/reconhub/recontools?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/recontools)](https://cran.r-project.org/package=recontools)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Tools to develop RECON packages

This is currently work in progress.

## Installation

### CRAN

Not yet on CRAN

### Development version

To install the most recent development version use:

```{r, eval = FALSE}
devtools::install_github("reconhub/recontools")
```

## What does it do?

### Package scaffolding

When starting a new RECON package, you can use `init_package` to quickly create default package structure:

```{r, eval = FALSE}
# from within your session
recontools::init_package("mynewpackage")

# you can also set a specific path for the new package
recontools::init_package("mynewpackage", path = "my_new_package_dir")

# you can also disable the CRAN checks
recontools::init_package("mynewpackage", check_cran_name = FALSE)
```

In case you want to create a new package from the command line, run:

```
Rscript -e "recontools::init_package('mynewpackage')"
```
Please note that using `Rscript` creates all optional components (like the MIT license) without asking.

`init_package` currently does the following:

* Checks if the package name is valid and already taken on CRAN
* Initializes a git repository, if not already present
* Creates default `.Rbuildignore` and `.gitignore` files
* Creates an `R` directory
* Creates a default `DESCRIPTION` file
* Adds an MIT License (asks for it)
* Adds `testthat` tests
* Adds a code of conduct (from the `devtools` package)
* Creates a default `README.Rmd`
* Creates a sample vignette
* Adds travis CI + codecov (asks for it)
* Adds appveyor (asks for it)
* Adds a default `.lintr` file
* Adds a `NEWS.md` file
* Runs `devtools::document()`
* Creates a `pkgdown` `docs` folder

### Package checks

You can also run package checks for a given package.

```{r, eval = FALSE}
# from within your session in a package directory
recontools::check_package()

# to enable goodpractice::gp checks do
recontools::check_package(run_gp = TRUE)
```

Currently, `check_package` does the following:

```{r}
recontools::check_package(run_gp = FALSE)
```

